Technical Paper Proposal: \\ Placement Algorithms for Heterogenous FPGAs

### 2024-09-09 docs/proposal/proposal.tex
more doc work

@@

    \item \textbf{EDA}: Electronic Design Automation
    \begin{itemize}[label={--}, left=0.25cm]
        \item Proprietary software for FPGA and VLSI development:
        \begin{itemize}[label={$\cdot$}, left=0.25cm]
            \item Xilinx - Vivado (Design + Simulation) + Vitis (HLS + PL-PS codesign)
            \item Altera - Quartus (Design) + ModelSim (Simulation)
            \item Synopsis (VLSI)
            \item Cadence (VLSI)
        \end{itemize}
        \item Open source software for FPGA development:
        \begin{itemize}[label={$\cdot$}, left=0.25cm]
            \item VTR: a PNR tool popular amongst researchers who study placement techniques
            \item OSS-CAD: a full-flow software suite that includes ABC synthesis, Yosys synthesis, Yosys nextpnr.
            \item AMF-Placer (Analytical Placer)
            \item DREAMPlace (VLSI) + DREAMPlaceFPGA
            \item RapidLayout (Hard Block Placer for Systolic Arrays)
            \item RapidStream (HLS Placer)
            \item RapidWright: Semi-open source API that provides backend access to Xilinx Vivado EDA using design checkpoints.
        \end{itemize}
    \end{itemize}

@@

\newpage
\bibliographystyle{ieeetr}
\nocite{*}
\bibliography{
    references/surveys,
    references/fpga_placement,
    references/vlsi_placement,
}

>>>>

\section{Proposal}

@@

    \item \textbf{EDA}: Electronic Design Automation
    \begin{itemize}[label={--}, left=0.25cm]
        \item Proprietary software for FPGA and VLSI development:
        \begin{itemize}[label={$\cdot$}, left=0.25cm]
            \item Xilinx - Vivado (Design + Simulation) + Vitis (HLS + PL-PS codesign)
            \item Altera - Quartus (Design) + ModelSim (Simulation)
            \item Synopsis (VLSI)
            \item Cadence (VLSI)
        \end{itemize}
        \item Open source software for FPGA development:
        \begin{itemize}[label={$\cdot$}, left=0.25cm]
            \item VTR: a PNR tool popular amongst researchers who study placement techniques
            \item OSS-CAD: a full-flow software suite that includes ABC synthesis, Yosys synthesis, Yosys nextpnr.
            \item AMF-Placer (Analytical Placer)
            \item DREAMPlace (VLSI) + DREAMPlaceFPGA
            \item RapidWright: Semi-open source API that provides backend access to Xilinx Vivado EDA using design checkpoints.
            \item RapidLayout: Hard Block Placer for Systolic Arrays. Built with RapidWright.
            \item RapidStream: HLS Placer. Built with RapidWright.
        \end{itemize}
    \end{itemize}

@@

\newpage
\bibliographystyle{ieeetr}
\nocite{*}
\bibliography{
    references/surveys,
    references/rapidwright,
    references/fpga_placement,
    references/vlsi_placement,
}
